Supplementary Material for \emph{A Guide to Pre-processing High-Frequency Animal Tracking Data}

### 2021-02-11 docs/ms_atlas_preproc_supplement.tex
add new tex and pdf
add pdfs and tex

% \IfFontExistsTF{Palatino}{\setmainfont[]{Palatino}}{} 
\usepackage{mathpazo}
\usepackage{helvet}
% \IfFontExistsTF{Arial}{\setsansfont[]{Arial}}{}
% \IfFontExistsTF{Fira Code}{\setmonofont{Fira Code}}

@@

\begin{figure}
\centering
\includegraphics{figures/fig_calib_residence.png}
\caption{Classifying thinned data into residence patches yields robust estimates of the duration of known stops. The island of Griend (53.25\(^{\circ}\)N, 5.25\(^{\circ}\)E) is shown in beige. Residence patches (green polygons; function parameters in text) correspond well to the locations of known stops (purple crossed-squares). However, the algorithm identified all areas with prolonged residence, including those which were not intended stops (n = 12; green polygons without crossed-squares). The algorithm also failed to find two stops of 6 and 15 seconds duration, since these were lost in the data thinning step (crossed-square without green polygon shows one of these). The area shown is the lower rectangle in Fig. 1.3.}
\end{figure}

>>>>

% \IfFontExistsTF{Palatino}{\setmainfont[]{Palatino}}{} 
\usepackage{mathpazo}
\usepackage{helvet}
\usepackage{inconsolata}
% \IfFontExistsTF{Arial}{\setsansfont[]{Arial}}{}
% \IfFontExistsTF{Fira Code}{\setmonofont{Fira Code}}

@@

\begin{figure}
\centering
\includegraphics{figures/fig_calib_residence.png}
\caption{Classifying thinned data into residence patches yields robust estimates of the duration of known stops. The island of Griend (53.25\(^{\circ}\)N, 5.25\(^{\circ}\)E) is shown in beige. Residence patches (green polygons; function parameters in text) correspond well to the locations of known stops (purple triangles). However, the algorithm identified all areas with prolonged residence, including those which were not intended stops (n = 12; green polygons without triangles). The algorithm also failed to find two stops of 6 and 15 seconds duration, since these were lost in the data thinning step (triangle without green polygon shows one of these). The area shown is the lower rectangle in Fig. 1.3.}
\end{figure}
